USER GUIDE 

1. BEFORE RUNNING THIS FILE, RUN THE RUN_ME_FIRST.R SCRIPT

2. TO RUN THIS PROJECT WITH YOUR OWN PRODUCTION AND FINANCIAL DATA, REPLACE THOSE FILES IN THE STRESS TEST INPUT FOLDER : 
  - abcd_stress_test_input.csv 
  - prewrangled_financial_data_stress_test.csv

-----------------------------------

```{r}
library(r2dii.climate.stress.test)
source(here::here("utils.R"))
```

## Define project parameters

```{r}
st_input_path <- here::here("st_input") 
st_output_path <- here::here("st_output")


cat(paste("The TRISK input path is located at :\n", st_input_path))
cat("\n\n")
cat(paste("The TRISK output path is located at :\n", st_output_path))
```

Switch between legacy and main inputs.

Leave default for latest version (recommended). Edit with "st_input_legacy"if working with legacy data

```{r}
convert_colnames_legacy_to_new(
  data_source=here::here("st_input_main"), 
  data_target=st_input_path
  )
```

## Explore possible trisk parameters

### Possible model parameters

```{r}
r2dii.climate.stress.test::stress_test_arguments
```

### Possible scenario parameters

According to the scenario datasets located in st_input those combinations of scenarios are possible for the matching sectors:

```{r}
possible_trisk_combinations <- r2dii.climate.stress.test::get_scenario_geography_x_ald_sector(st_input_path)
possible_trisk_combinations |>
  dplyr::distinct(baseline_scenario, shock_scenario)
```

Replace the values for baseline scenario and shock scenario to list their possible geographies :

```{r}
possible_trisk_combinations |>
  dplyr::filter(
    baseline_scenario == "NGFS2023GCAM_NDC", # EDIT VALUE
    shock_scenario == "NGFS2023GCAM_NZ2050" # EDIT VALUE
    ) |>
  dplyr::distinct(scenario_geography)

```

## Run TRISK

Set parameters

```{r}
# scenario parameters
baseline_scenario <- "NGFS2023GCAM_NDC" # EDIT VALUE
shock_scenario <- "NGFS2023GCAM_NZ2050" # EDIT VALUE
scenario_geography <- "Global" # EDIT VALUE
  
# model parameters  
discount_rate <- c(0.1) # EDIT VALUE
shock_year <- c(2035) # EDIT VALUE
risk_free_rate <- c(0.05) # EDIT VALUE
# .... Add more parameters definition here and in the run_trisk() function call below

```

Run the model

```{r}
run_trisk(
  input_path=st_input_path,
  output_path=st_output_path,
  baseline_scenario=baseline_scenario,
  shock_scenario=shock_scenario,
  scenario_geography=scenario_geography,
  discount_rate = discount_rate,
  shock_year = shock_year,
  risk_free_rate = risk_free_rate
)
cat(paste("Run complete, find results in the folder named with the most recent date in\n\n", st_output_path))
```
